Measurement and Probability in Fuzzy Quantum Theories

### 2017-03-05 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

\begin{lemma}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~A
frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
the following properties:
\begin{itemize}
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
we have $1=\sum_{i=0}^{2}f\left(\ket{\psi_{i}}\right)$.
\end{itemize}
Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfies the above properties, $f$ must be a frame function.\end{lemma}

@@

\begin{tabular}{ccc|cccc} 
\br 
\multicolumn{3}{c}{Operators} & \multicolumn{4}{c}{Common eigenbasis} \\
\mr 
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
\br 
\end{tabular} 
\end{table}
Since observables in equation~(\ref{eq:MerminSquare}) are not projectors,
if we want to reformulate the above argument in the language of quantum
probability measures, we first need to find the common eigenbasis
of each row and column, and consider the projectors to each eigenvectors.
Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
Then, proving the Kochen-Specker theorem is proving there is no function~$\set{\proj{\psi}}{\ket{\psi}\in\mathcal{T}_{24}}$
to $\left\{ 0,1\right\} $.

>>>>

\begin{thm}\label{thm:frame-function}\cite{gleason1957,peres1995quantum,RichmanBridges1999}~A
frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
the following properties: 
\begin{itemize}
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$. 
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{2}$,
we have $1=\sum_{i=0}^{2}f\left(\ket{\psi_{i}}\right)$. 
\end{itemize}
Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfies the above properties, $f$ must be a frame function.\end{thm}

@@

\begin{tabular}{ccc|cccc} 
\br 
\multicolumn{3}{c}{Operators} & \multicolumn{4}{c}{Common eigenbasis} \\
\mr 
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
\br 
\end{tabular} 
\end{table}
Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
if we want to reformulate the above argument in the language of quantum
probability measures, we first need to find the common eigenbasis
of each row and column, and consider the projections to each eigenvectors.
Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
The Kochen-Specker theorem could then be proved by showing there is
no function~$v:\events'\rightarrow\left\{ 0,1\right\} $satisfying
equation~(\ref{eq:Kochen-Specker-Rules}), where 
\[
\events'=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}\textrm{ is a family of mutually orthogonal projections}}\textrm{ .}
\]
This kind of $v$ is actually a quantum cryptodeterministic measure.
By theorem~\ref{lemma:classical-probability-measures}, the quantum
cryptodeterministic measure~$v$ exists if and only if there exists
a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $.
